Location of Bivalve Farms

### 2021-02-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished marine bivalve data quality

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA")

@@

us_aqua_species <- us_aqua %>%
   dplyr::filter(!is.na(species)) %>%
  dplyr::filter(!(species %in% c("finfish", "Atlantic salmon", "Atlantic cod", "Seaweed", "Shrimp", "Coral", "clam seed, oyster seed", "Gelidium spp., Macrocystis pyrifera, M. angustifolia, M. intergrifolia, Pelagophycus spp. Euchema uncinatum (male plants only)", "oyster seed", "In progress", "Not Available", "Hatchery", "softshell", "softshell, butter", "softshell, varnish", "butter"))) %>%
  dplyr::filter(state != "Federal waters") %>%
  dplyr::filter(!(status %in% c(NA, "Pending", "Restricted-Relay", "Not Available", "Conditional Closure", "Prohibited"))) %>%
dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York")))

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA")

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c)

@@

## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datatsets. 
eu_fao_countries <- eu_active_na %>%
  dplyr::filter(!(COUNTRY %in% c("France", "United Kingdom", "Denmark")))

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC"
  )) %>%
  dplyr::select(-COUNTRY)

@@

## Spain
https://servicio.pesca.mapama.es/acuivisor/
 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

@@

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
  mutate(iso3c = "ESP")

@@

farms_jey <- data.frame(lat = c(49.17300525845569, 49.22644208989364, 49.17293132589725, 49.231523271584344, 49.20231914535721),
                        lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
  mutate(iso3c = "JEY")

@@

farms_ggy_final <- farms_ggy %>%
  mutate(iso3c = "GGY")

@@

farms_svn_final <- farms_svn %>%
  mutate(iso3c = "SVN")

@@

farms_hrv_final <- farms_hrv %>%
  mutate(iso3c = "HRV")

@@

farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.910246),
                        lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
  mutate(iso3c = "CUB")

@@

## Taiwan
 - I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. We will allocate the cells equally along the coastline (like we did for shrimp).
 - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/

@@

gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")

 TWN_shp <- gadm %>%
  filter(GID_0 == "TWN") %>%
  st_transform(., food_crs) %>%
  mutate(Region = 1)
 mapview(TWN_shp)

st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")

twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")

plot(fake_raster)
plot(twn_reg_ras)

writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_spatial <- as(TWN_shp, "Spatial")

twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)

plot(twn_coast)
cellStats(twn_coast, "sum") #464.63

# filter to include >0 <1, o.w. NA

twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
  mutate(iso3c = "TWN") %>%
  dplyr::select(lon=x, lat=y, iso3c)

farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))

twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)
```

@@

```{r}
farms_pyf <- data.frame(lat = c(-17.349601342130857, -18.50754847683744),
                        lon = c(-138.40992718639146, -136.38467411084235)) %>%
  mutate(iso3c = "PYF")

@@

farms_ind_final <- farms_ind %>%
  mutate(iso3c = "IND")

@@

farms_tha <- data.frame(do.call(rbind, st_geometry(tha_pts_latlon))) 
names(farms_tha) <- c("lon", "lat")
farms_tha <- farms_tha %>%
  mutate(iso3c="THA")

@@

```{r}
farms_idn <- data.frame(lat = c(3.2182751224662542, -5.964150035506321, -6.2646012824936275, -6.75680397048712, -6.975573928794459, -4.984732967006041, 0.889089620526810, -3.436748178542682, -5.142358892765042),
                        lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
  mutate(iso3c = "IDN")

@@

farms_rus <- data.frame(lat = c(43.053493816917545),
                        lon = c(131.95698485517275)) %>%
  mutate(iso3c = "RUS")

@@

farms_prk_final <- farms_prk %>%
  mutate(iso3c = "PRK")

@@

farms_bra_final <- farms_bra %>%
  mutate(iso3c = "BRA")

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL")

@@

farms_mys <- data.frame(lat = c(4.074359958576369),
                        lon = c(100.73343376478226)) %>%
  mutate(iso3c = "MYS")

@@

farms_khm <- data.frame(lat = c(11.069927194335508),
                        lon = c(103.64594001534627)) %>%
  mutate(iso3c = "KHM")

@@

farms_hkg <- data.frame(lat = c(22.48384043911231),
                        lon = c(113.98143449612208)) %>%
  mutate(iso3c = "HKG")

@@

@@

write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)

>>>>

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0).

Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).

Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)

Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location.

Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 1.0)

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 1.0)

@@

us_aqua_species <- us_aqua %>%
   dplyr::filter(!is.na(species)) %>%
  dplyr::filter(!(species %in% c("finfish", "Atlantic salmon", "Atlantic cod", "Seaweed", "Shrimp", "Coral", "clam seed, oyster seed", "Gelidium spp., Macrocystis pyrifera, M. angustifolia, M. intergrifolia, Pelagophycus spp. Euchema uncinatum (male plants only)", "oyster seed", "In progress", "Not Available", "Hatchery", "softshell", "softshell, butter", "softshell, varnish", "butter"))) %>%
  dplyr::filter(state != "Federal waters") %>%
  dplyr::filter(!(status %in% c(NA, "Pending", "Restricted-Relay", "Not Available", "Conditional Closure", "Prohibited"))) %>%
dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York"))) ## filter out the states we already have

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 1.0)

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 1.0)

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 1.0)

@@

## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datasets. 
eu_fao_countries <- eu_active_na %>%
  dplyr::filter(!(COUNTRY %in% c("France", "United Kingdom", "Denmark")))

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 1.0)

@@

## Spain
TODO: Figure out how to download exact locations

https://servicio.pesca.mapama.es/acuivisor/
 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

@@

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
  mutate(iso3c = "ESP") %>%
  mutate(data_quality = 0.333)

@@

farms_jey <- data.frame(lat = c(49.17300525845569, 49.22644208989364, 49.17293132589725, 49.231523271584344, 49.20231914535721),
                        lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
  mutate(iso3c = "JEY") %>%
  mutate(data_quality = 1.0)

@@

farms_ggy_final <- farms_ggy %>%
  mutate(iso3c = "GGY") %>%
  mutate(data_quality = 0.333)

@@

farms_svn_final <- farms_svn %>%
  mutate(iso3c = "SVN") %>%
  mutate(data_quality = 0.333)

@@

farms_hrv_final <- farms_hrv %>%
  mutate(iso3c = "HRV") %>%
  mutate(data_quality = 0.333)

@@

farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.910246),
                        lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 0.667)

@@

## Taiwan
- I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. I will randomly place a point in the Qigu lagoon (see article). 
 - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/

@@

farms_twn <- data.frame(lat = c(23.12185817551473),
                        lon = c(120.05482898155049)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 0.0)

write_csv(farms_twn, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))

## visualize it 
farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

OLD WAY: 
```{r}

# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
# 
#  TWN_shp <- gadm %>%
#   filter(GID_0 == "TWN") %>%
#   st_transform(., food_crs) %>%
#   mutate(Region = 1)
#  mapview(TWN_shp)
# 
# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
# 
# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
# 
# 
# plot(fake_raster)
# plot(twn_reg_ras)
# 
# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# 
# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
# 
# twn_spatial <- as(TWN_shp, "Spatial")
# 
# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
# 
# plot(twn_coast)
# cellStats(twn_coast, "sum") #464.63
# 
# # filter to include >0 <1, o.w. NA
# 
# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
#   mutate(iso3c = "TWN") %>%
#   dplyr::select(lon=x, lat=y, iso3c)
# 
# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
# 
# 
# write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
# 
# 
# twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))
# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_twn)
```

@@

```{r}
farms_pyf <- data.frame(lat = c(-17.349601342130857, -18.50754847683744),
                        lon = c(-138.40992718639146, -136.38467411084235)) %>%
  mutate(iso3c = "PYF") %>%
  mutate(data_quality = 1.0)

@@

farms_ind_final <- farms_ind %>%
  mutate(iso3c = "IND") %>%
  mutate(data_quality = 0.333)

@@

farms_tha <- data.frame(do.call(rbind, st_geometry(tha_pts_latlon))) 
names(farms_tha) <- c("lon", "lat")
farms_tha <- farms_tha %>%
  mutate(iso3c = "THA") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_idn <- data.frame(lat = c(3.2182751224662542, -5.964150035506321, -6.2646012824936275, -6.75680397048712, -6.975573928794459, -4.984732967006041, 0.889089620526810, -3.436748178542682, -5.142358892765042),
                        lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 0.667)

@@

farms_rus <- data.frame(lat = c(43.053493816917545),
                        lon = c(131.95698485517275)) %>%
  mutate(iso3c = "RUS") %>%
  mutate(data_quality = 0.0)

@@

farms_prk_final <- farms_prk %>%
  mutate(iso3c = "PRK") %>%
  mutate(data_quality = 0.333)

@@

farms_bra_final <- farms_bra %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 0.333)

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 0.333)

@@

farms_mys <- data.frame(lat = c(4.074359958576369),
                        lon = c(100.73343376478226)) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 0.0)

@@

farms_khm <- data.frame(lat = c(11.069927194335508),
                        lon = c(103.64594001534627)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 0.0)

@@

farms_hkg <- data.frame(lat = c(22.48384043911231),
                        lon = c(113.98143449612208)) %>%
  mutate(iso3c = "HKG") %>%
  mutate(data_quality = 0.667)

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

@@

write.csv(all_farms_1, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)

write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv"))
```
